Process-based phenotypes: an application to the Cellular Phenotype Ontology

### 2011-11-21 trunk/paper/drinking.tex

% \subsection{Problem statement 3}
% A phenotype such as {\em Increased drinking behavior} is used for the
% annotation of phenotypes in mouse and other species.

% Different meanings:
% \begin{itemize}
% \item amount of substance increased over fixed period (e.g., 24h)
% \item amount of substance per drinking act is increased
% \item amount of time spent drinking over fixed period is increased
% \item amount of time spent per drinking act is increased
% \item number of drinking acts per fixed period increased
% \item variety of substances that organism drinks is increased (over
%   24h, per drinking act)
% \item substance flow during drinking increased
% \end{itemize}

% more than just these aspects of ``drinking behavior'' can be increased

@@

A first kind of abnormality of regulatory processes are {\em abnormal
  temporal distribution patterns} of a process. The most common
abnormal distribution pattern

We use PATO's {\em frequency} class to define {\em Abnormal frequency
  of occurrence of $X$} as a subclass of an {\em Abnormality of the
  regulation of $X$}.

>>>>

@@

A first kind of abnormality of regulatory processes are {\em abnormal
  temporal distribution patterns} of a process. In these
abnormalities, the {\em way} in which processes of a particular kind
are temporally distributed is abnormal.  The most common abnormal
distribution pattern is an increased or decreased frequency, and we
use PATO's {\em frequency} class to define {\em Abnormal frequency of
  occurrence of $X$}.
% as a subclass of an {\em Abnormality of the regulation of $X$}.
